Fixing Vulnerabilities Hinders Maintainability

### 2020-01-27 paper/icpc20.tex
more writing on results + cleaning

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.5\textwidth]{figures/maintainability_severity.pdf}
 	\caption{Maintainability difference by the vulnerabilities severity.}
	\label{fig:severity}

@@

>>>>

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.45\textwidth]{figures/maintainability_severity.pdf}
 	\caption{Maintainability difference by the vulnerabilities severity.}
	\label{fig:severity}

@@

For the vulnerabilities identified with CVE(s), we scraped NVD to retrieve 
their severity levels. In total, we obtained severity scores for $574$ 
vulnerabilities: $121$ \emph{HIGH}, $423$ \emph{MEDIUM} and $30$ \emph{LOW}. 
Figure~\ref{fig:severity} presents the impact
of security patches per severity level on the maintainability of open-source 
software. Although with no statistical significance, we observe that 
vulnerabilities with higher severity levels (\emph{HIGH} and \emph{MEDIUM}) have more negative impact than the \emph{LOW} severity level on the
maintainability of software.
